### 2022-05-29 README.Rmd
update documentation
update badges

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis-CI Build Status](https://travis-ci.com/slu-openGIS/areal.svg?branch=master)](https://travis-ci.com/slu-openGIS/areal)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
[![Downloads](http://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](http://www.r-pkg.org/pkg/areal)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
[![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)

@@

### What is New in v0.1.6?
This version contains updates under the hood to make it compatible with `dplyr`'s v1.0 release!

>>>>

[![R build status](https://github.com/slu-openGIS/areal/workflows/R-CMD-check/badge.svg)](https://github.com/slu-openGIS/areal/actions)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
[![Downloads](http://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](http://www.r-pkg.org/pkg/areal)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
[![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)

@@
